Linear analysis of the vertical shear instability in astrophysical disks

### 2015-02-07 numerical.tex
major updating

\subsection{Critical thermal relaxation timescale}
We test our estimate for the maximum thermal relaxation timescale 
$\beta_\mathrm{crit}$ for the fundamental
VSI (Eq. \ref{iso_vsi_cond}). We use the previous disk
parameters as a fiducial case and vary $q\in[-0.2,-1.2]$,
$\gamma\in[1.2,2.0]$ and $\epsilon\in[]$
separately. The numerically-obtained $\beta_\mathrm{crit}$ is shown in
Fig. \ref{bcrit_compare} in comparison with Eq. \ref{iso_vsi_cond}.

@@

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0.cm 0cm
  0cm]{figures/bcrit_compare_q.ps} 
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0.0cm 0cm
  0.8cm]{figures/bcrit_compare_g.ps} 
  \caption{Dependence of the upper limit to the thermal relaxation timescale
    $\beta_\mathrm{crit}$ for the fundamental VSI mode on disk
    parameters. The fiducial parameters are $\Gamma=1.011$,
    $\gamma=1.4$ and $(p,q,\epsilon)=(-1.5,-1,0.05)$. Top: varying
    $q\in[-1.2,-0.2]$; middle: varying $\gamma\in[1.2,2.0]$; bottom:
    varying $\epsilon\in[]$. The perturbation wavenumber is
    $\khat=20$. {\bf still need variable epsilon case}
    \label{bcrit_compare}}  
\end{figure}

>>>>

\subsection{Critical thermal relaxation timescale}
We test our estimate for the maximum thermal relaxation timescale 
$\beta_\mathrm{crit}$ for the fundamental
VSI (Eq. \ref{iso_vsi_cond}). We use the previous disk
parameters as a fiducial case and vary $q\in[-0.2,-1.2]$,
$\gamma\in[1.2,2.0]$ and $\epsilon\in[0.02,0.1]$
separately. The numerically-obtained $\beta_\mathrm{crit}$ is shown in
Fig. \ref{bcrit_compare} in comparison with Eq. \ref{iso_vsi_cond}.

@@

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0.cm 0cm
  0cm]{figures/bcrit_compare_q.ps} 
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0.0cm 0cm
  0.8cm]{figures/bcrit_compare_g.ps}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0.0cm 0cm
  0.8cm]{figures/bcrit_compare_e.ps} 
  \caption{Dependence of the upper limit to the thermal relaxation timescale
    $\beta_\mathrm{crit}$ for the fundamental VSI mode on disk
    parameters. The fiducial parameters are $\Gamma=1.011$,
    $\gamma=1.4$ and $(p,q,\epsilon)=(-1.5,-1,0.05)$. Top: varying
    $q\in[-1.2,-0.2]$; middle: varying $\gamma\in[1.2,2.0]$; bottom:
    varying $\epsilon\in[0.02,0.1]$. The perturbation wavenumber is
    $\khat=10$. 
    \label{bcrit_compare}}  
\end{figure}
